Synthesizing Quotient Lenses

### 2018-03-12 papers/QuotientLenses/main.tex
evaluation text changes

  \item Does the increase in expressivity gained from synthesizing from QREs
  permit synthesis of more useful lenses than existing approaches.  \bcp{Is
    this really an interesting empirical question?  Seems obvious, from the
    arguments we made in Section 2 and the intro.}\afm{I'm happy to remove it}

@@

To evaluate our QRE implementation, we constructed a set of lens synthesis tasks
drawn from two sources:
\begin{enumerate}
\item 39 of our benchmarks were adapted from the evaluation of the original
  Optician system.  These benchmarks are a combination of custom benchmarks,
  benchmarks derived from FlashFill~\cite{flashfill}, and benchmarks
  derived from Augeas~\cite{augeas2}. In the pre-QRE version of
  Optician, many of these data formats had to be modified to work with the
  bijectivity constraints that Optician required.  For instance, when one format
  permits whitespace where the other does not allow it, the original versions of
  benchmark formats were modified to allow more whitespace, thereby restoring
  bijectivity.  With the new QRE support, we were able to remove these
  alterations when porting these benchmarks.  (This experience alone suggests
  that QREs make the lens development process easier.)

\item The remaining eight benchmarks were derived from datasets found at 
  data.gov. These datasets include census
  population data, wage comparison data, demographics statistics data and
  crime index data. We chose these datasets since they were stored in XML, CSV
  and RDF formats which are more easily specified using regular expressions than
  plain text or PDF documents.  \BCP{Besides differing formats, why did we
    include these eight new 
    ones?  Are they significantly different (more complex, exercising
    different features of the synthesis algorithm or QRE syntax,
    ...)?}\afm{Solomon, could you fill this out?}
    \sam{Well these data formats were the ones I was playing with before we got
    the Augeus and flashfill examples. I chose them simply because they had
    formats which could be expressed using regular expressions. They basically
    use the same QREs as the flashfill and augeus examples, mostly the project
    QRE. The fields in these files are occur in the same order in each record;
    we tried using the perm combinator anyways but the synthesis algorithm took
    too long. I do not think that they are significantly different from the
    flashfill and augues examples.}\afm{So would it be appropriate to say it was
    these were merely the first examples in the data.gov website whose languages
    are regular?}\BCP{Or would anything be lost by just deleting them?  It
    seems like we're tying ourselves in knots at bit trying to explain how
    they relate to the others and what is interesting about them, when the
    answer seems to be they don't and nothing.}
\end{enumerate}

@@

\subsection{Increasing Expressivity}

The pre-QRE version of Optician was only able to synthesize fully bijective data
transformations. Synthesizing from QREs loosens that restriction, making it
possible to synthesize data transformations involving bijections with
canonization functions. Because Optician could previously only synthesize
bijective lenses, some of the data formats in the example suite were modified to
include additional fields containing information should should be canonized from
the other format. In total, 12 of Optician's original benchmarks and 3 of the
data.gov benchmarks would require such additional fields when input to Optician
without QREs.

>>>>

@@

To evaluate our QRE implementation, we adapted 39 lens synthesis tasks from the
benchmark suite of the original Optician system. These benchmarks are a
combination of custom benchmarks, benchmarks derived from
FlashFill~\cite{flashfill}, and benchmarks derived from Augeas~\cite{augeas2}.
In the pre-QRE version of Optician, many of these data formats had to be
modified to work with the bijectivity constraints that Optician required. For
instance, when one format permits whitespace where the other does not allow it,
the original versions of benchmark formats were modified to allow more
whitespace, thereby restoring bijectivity (but altering the data format). With
the new QRE support, we were able to remove these alterations when porting these
benchmarks. (This experience alone suggests that QREs make the lens development
process easier.)

@@
